---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nse2r

> Fetch data from the National Stock Exchange, India.

<!-- badges: start -->
[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/nse2r)](https://cran.r-project.org/package=nse2r)
[![Travis-CI Build
Status](https://travis-ci.org/rsquaredacademy/nse2r.svg?branch=master)](https://travis-ci.org/rsquaredacademy/nse2r)
[![AppVeyor Build
Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/nse2r?branch=master&svg=true)](https://ci.appveyor.com/project/rsquaredacademy/nse2r)
[![Coverage
Status](https://img.shields.io/codecov/c/github/rsquaredacademy/nse2r/master.svg)](https://codecov.io/github/rsquaredacademy/nse2r?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Overview

[NSE](https://www.nseindia.com/) (National Stock Exchange) is the leading stock exchange of India, located in the city of Mumbai. While users can manually download data from NSE through a browser, importing this data into R is then cumbersome. The nse2r R package implements the retrieval of data from NSE and aims to reduce the pre-processing steps needed in analyzing such data.

nse2r is inspired by and a port of the Python package [nsetools](https://nsetools.readthedocs.io/en/latest/). The authors and contributors for this R package are not affiliated with NSE and NSE does not offer support for this R package.

With nse2r, you can fetch the following data related to:

- stocks
    - quote for a given stock
    - symbol & name
    - check validity
    - most actively traded stocks in a month
    - 52 week high/low
    - top gainers/losers for the last trading session
- index
    - list indices
    - check validity
    - fetch indices quote
- futures & options
    - lot size
    - top gainers/losers for the last trading session
- pre open data
    - nifty
    - nifty bank
    - nifty futures & options
- indices advances & declines

## Installation

You can install the development version of nse2r from [GitHub](https://github.com/rsquaredacademy/nse2r/) with:

```{r cran-install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("rsquaredacademy/nse2r")
```

## Articles

- [Introduction to nse2r](https://nse2r.rsquaredacademy.com/articles/introduction-to-nse2r.html)

## Usage

```{r load_nse2r, echo=FALSE, message=FALSE, warning=FALSE}
library(nse2r)
```

nse2r uses consistent prefix `nse_` for easy tab completion.

- `nse_index_` for index 
- `nse_stock_` for stocks
- `nse_fo_` for futures and options
- `nse_preopen_` for preopen data

### Index

##### Fetch Indices Quote

```{r index_quote}
nse_index_quote()
```

### Stock

##### Top gainers for the last trading session.

```{r stock_top_gainers}
nse_stock_top_gainers()
```

##### Stocks that have touched their 52 week highs during the day

```{r stock_year_high}
nse_stock_year_high()
```

##### Most actively traded stocks in a month

```{r stock_most_traded}
nse_stock_most_traded()
```

### Futures & Options

##### Top futures and options gainers for the last trading session.

```{r fo_top_gainers}
nse_fo_top_gainers()
```

Please note that the 'nse2r' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
