---
title: "introduction-to-nsetools"
author: "Aravind Hebbali and Lokesh Atreja"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction-to-nsetools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r load_httptest, include=FALSE}
library(httptest)
start_vignette("nse")
```

[NSE](https://www.nseindia.com/) (National Stock Exchange) is the leading stock exchange of India, located in the city of Mumbai. While users can manually download data from NSE through a browser, importing this data into R is then cumbersome. The nsetools R package implements the retrieval of data from NSE and aims to reduce the pre-processing steps needed in analyzing such data.

nsetools is inspired by and a port of the Python package [nsetools](https://nsetools.readthedocs.io/en/latest/). The authors and contributors for this R package are not affiliated with NSE and NSE does not offer support for this R package.

With nsetools, you can fetch the following data related to:

- stocks
    - quote for a given stock
    - symbol & name
    - check validity
    - most actively traded stocks in a month
    - 52 week high/low
    - top gainers/losers for the last trading session
- index
    - list indices
    - check validity
    - fetch indices quote
- futures & options
    - lot size
    - top gainers/losers for the last trading session
- pre open data
    - nifty
    - nifty bank
    - nifty futures & options
- indices advances & declines


## Usage

nsetools uses consistent prefix `nse_` for easy tab completion.

- `nse_index_` for index 
- `nse_stock_` for stocks
- `nse_fo_` for futures and options
- `nse_preopen_` for preopen data

```{r load_nse}
library(nsetools)
```

## Stocks

Fetch most actively traded stocks in a month on NSE.

```{r stock_2}
nse_stock_most_traded()
```

Fetch top gainers for the last trading session.

```{r stock_4}
nse_stock_top_gainers()
```

Fetch top losers for the last trading session.

```{r stock_5}
nse_stock_top_losers()
```

Fetch stocks that have touched their 52 week highs during the day on NSE.

```{r stock_6}
nse_stock_year_high()
```

Fetch stocks that have touched their 52 week lows during the day on NSE.

```{r stock_7}
nse_stock_year_low()
```
## Index

List NSE indices.

```{r index_1}
nse_index_list()
```

NSE indices quote.

```{r index_2}
nse_index_quote()
```

Check if index is valid.

```{r index_3}
nse_index_valid("nify 50")
nse_index_valid("nifty 50")
```

## Futures & Options

Top futures and options gainers for the last trading session.

```{r fo_2}
nse_fo_top_gainers()
```

Top futures and options losers for the last trading session.

```{r fo_3}
nse_fo_top_losers()
```

## Preopen Data

Fetch data of pre open session of futures and options from NSE.

```{r po_1}
nse_preopen_fo()
```

Fetch data of pre open session of Nifty from NSE.

```{r po_2}
nse_preopen_nifty()
```

Fetch data of pre open session of Nifty Bank from NSE.

```{r po_3}
nse_preopen_nifty_bank()
```

## Advances & Declines

NSE indices advances & declines.

```{r ad}
nse_advances_declines()
```

```{r end_vignette, include=FALSE}
end_vignette()
```












